Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
small edit

Regarding gender grouping, both genders agree in the possible uses of chatbots,
so it seems not relevant at all. However, when we look at the plot containing
the sector differentiation, it is interesting to note that university teaching
staff are more likely to use chatbots for grades and FAQs compared to teaching
staff involved in other tertiary education institutions. This appears logical,
as the number of personal interactions with students in certain classes at the
university is smaller\footnote{Most university classes take place one or twice
  week, as opposed to daily classes with the same teacher in other tertiary
  education, and hold usually twice as many persons as the typical tertiary
  education class}, thus an automated grade notification tool for continuous
evaluation would be more beneficial.  Furthermore, the high student-to-teacher
ratios that university educators often face could be another reason why a higher
number of them are willing to use chatbots for FAQs, as this could reduce
misunderstandings and email (or face to face tutoring) overload from students.

>>>>

Regarding gender grouping, both genders agree in the possible uses of chatbots,
so it seems not relevant at all. However, when we look at the plot containing
the sector differentiation, it is interesting to note that university teaching
staff are more likely to use chatbots for grades and FAQs compared to teaching
staff involved in other tertiary education institutions. This appears logical,
as the number of personal interactions with students in certain classes at the
university is smaller\footnote{Most university classes take place once or twice
 a week, as opposed to daily classes with the same teacher in other tertiary
  education, and hold usually twice as many persons as the typical tertiary
  education class}, thus an automated grade notification tool for continuous
evaluation would be more beneficial.  Furthermore, the high student-to-teacher
ratios that university educators often face could be another reason why a higher
number of them are willing to use chatbots for FAQs, as this could reduce
misunderstandings and email (or face to face tutoring) overload from students.
